---
title: "iris tests"
author: "An Bui"
date: "11/7/2018"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### 0. Load in relevant packages
```{r set up code, message = FALSE}
library(tidyverse)
library(kableExtra)
library(dplyr)
```

#### 1. Data wrangling with the iris package.
```{r create a data frame to use}
# create a new data frame from iris, group by species
iris_new <- iris %>% 
  group_by(Species)
```

```{r make a summary table}
# create a new table using iris data
iris_simpl <- iris_new %>%
  # some summary statistics of interest
  summarize(
    mean_petal_l = round(mean(Petal.Length),2),
    mean_petal_w = round(mean(Petal.Width),2),
    sample_size = length(Species)
  )

# set a vector with table column names
table_columns = c("Species", "Mean petal length", "Mean petal width", "Sample size")

# set a vector for table caption
table_caption = c("**Table 1. Summary of iris petal measurements.** All measurements are in centimeters and come from the famous (Fisher's or Anderson's) iris dataset.")

kable(iris_simpl,
      col.names = table_columns,
      caption = table_caption) %>% 
  kable_styling(
      position = "center")
```
#### 2. Ask a question of the data.
Do iris species have different petal lengths?  
H~0~: There is no difference in mean petal lengths between the three iris species.  
H~A~: There is a difference in mean petal lengths between at least two iris species.  
You know that you're comparing three groups, so you can't use a t-test; rather, you'll use an ANOVA. However, you have some conditions to meet:  
- normal data  
- equal variances  
- continuous data  
- independence  
Independence and continuous data are already established, so now you have to figure out of the data are normally distributed and if they have equal variances.

First, make a histogram.
```{r make a histogram of petal length}
# write your labels
iris_hist_x = c("Petal length (cm)")
iris_hist_y = c("Frequency (n = 50)")
iris_hist_caption = expression(paste(bold("Figure 1. Histogram of iris petal lengths. "), "Data are normally distributed."))

# make a histogram of sepal length
iris_hist <- ggplot(iris_new, aes(x = Petal.Length)) +
  geom_histogram(bins = 10,
                 aes(fill = Species)) +
  facet_wrap(~ Species) +
  labs(x = iris_hist_x, y = iris_hist_y, caption = iris_hist_caption) +
  theme_bw() +
  theme(plot.caption = element_text(hjust = 0))

iris_hist

```
Then, make a qqplot.
```{r make a qqplot of petal length}
# write your labels
iris_qq_caption = expression(paste(bold("Figure 2. QQPlot of iris petal lengths. "), "There is a linear relationship between values drawn from a theoretically normally distributed population (x-axis) and sample values (y-axis), therefore data are normally distributed."))
### how do you make captions wrap????

# create your qqplot
iris_qq <- ggplot(iris, aes(sample = Petal.Length)) +
  geom_qq() +
  facet_wrap(~ Species) +
  labs(caption = iris_qq_caption) +
  theme_bw() +
  theme(plot.caption = element_text(hjust = 0))
  

iris_qq
```

In the end, you know that petal length is normally distributed from the histogram and the qqplot. Additionally, you know that your sample size is greater than 30, so the means of samples drawn from the population will be normally distributed following the CLT. Therefore, you can use a 
